Web Page Visualization Code

### 2024-09-01 Scripts - Data Cleaning and Visuals/CSV Cleaning.Rmd
finished the first hyp code

# Add a totals row
totals <- keywords_summary_df %>%
  summarize(
    newsgroup = "Total",
    Comments_with_Keywords = sum(Comments_with_Keywords),
    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
    Unique_Authors = sum(Unique_Authors),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Average_Relevancy_Score, na.rm = TRUE),
    Average_Thread_Relevancy = mean(Average_Thread_Relevancy, na.rm = TRUE)
  )

>>>>

total_unique_authors <- n_distinct(comments_in_keyword_threads$Author)

# Add a totals row
totals <- keywords_summary_df %>%
  summarize(
    newsgroup = "Total",
    Comments_with_Keywords = sum(Comments_with_Keywords),
    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
    Unique_Authors = total_unique_authors,
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Average_Relevancy_Score, na.rm = TRUE),
    Average_Thread_Relevancy = mean(Average_Thread_Relevancy, na.rm = TRUE)
  )

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
finished the first hyp code

```{r R Load Libraries, Directories, and Datasets}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(igraph)
library(ggraph)
library(tidytext)
library(topicmodels)
library(visNetwork)
library(RColorBrewer)

@@

```{r Filtering For Relevancy}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Calculate the minimum and maximum of the 'Thread_Relevancy' column
min_value <- min(all_threads$Thread_Relevancy, na.rm = TRUE)
max_value <- max(all_threads$Thread_Relevancy, na.rm = TRUE)

@@

```{r}
# Filter out Quartile 1
filtered_threads <- all_threads %>%
  filter(Quartile != "Q1")

@@

```{r Relevancy Filtered Descriptive Statistics}
library(sjPlot)

# Step 1: Group by newsgroup and calculate required statistics, including comment relevancy
keywords_summary_df <- filtered_comments %>%
  group_by(newsgroup) %>%
  summarize(
    Unique_Authors = n_distinct(Author),
    Comments_with_Keywords = sum(Relevancy > 0),
    Conversations_Mentioned_In = n_distinct(Thread.ID),
    Total_Comments_In_Threads = n(),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Relevancy, na.rm = TRUE)
  )

@@

# Theme Prevelance Hypothesis
```{r Data Preparation}
library(topicmodels)
library(tm)
library(SnowballC)
library(tidytext)
library(dplyr)
library(ggplot2)
library(igraph)
library(ggraph)

# Data preparation: Select relevant text data
comments_corpus <- Corpus(VectorSource(all_comments$Full.Text)) # Replace 'Content' with the actual column name containing text data

@@

```{r How Many Topics, eval=FALSE, include=FALSE}
library(ldatuning)

# Sample a smaller subset of the DTM
set.seed(123)
sample_indices <- sample(1:nrow(dtm), 1000)  # Reduce size to speed up
sampled_dtm <- dtm[sample_indices, ]

# Optimize LDA to find the best number of topics
set.seed(123)
result <- FindTopicsNumber(
  sampled_dtm,
  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
  metrics = c("Griffiths2004", "Deveaud2014"),  # Use fewer metrics
  method = "Gibbs",
  control = list(seed = 123, iter = 500),  # Fewer iterations for quicker results
  mc.cores = 6L,
  verbose = TRUE
)

@@

```{r LDA Model}
set.seed(123) # Set seed for reproducibility
lda_model <- LDA(dtm, k = 8, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
```

@@

```{r Co-occurrence Network Analysis}
# Step 1: Filter out terms with lower frequencies or less importance
# You may set a threshold for filtering less relevant terms
term_frequency <- rowSums(co_occurrence) # Calculate term frequency
threshold <- quantile(term_frequency, 0.9) # Set threshold for top 10% most frequent terms
filtered_terms <- which(term_frequency > threshold)
filtered_co_occurrence <- co_occurrence[filtered_terms, filtered_terms]

# Step 2: Create graph object with filtered terms
graph <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)

# Step 3: Simplify the graph to avoid self-loops and redundant edges
graph <- simplify(graph)

# Step 4: Visualize the co-occurrence network with improved settings
set.seed(123)  # For reproducibility
ggraph(graph, layout = 'fr') + 
  geom_edge_link(aes(edge_alpha = weight), show.legend = FALSE, edge_width = 0.2) + 
  geom_node_point(color = "blue", size = 4) + 
  geom_node_text(aes(label = name), repel = TRUE, max.overlaps = 20) + # Increase max.overlaps for ggrepel
  theme_void() +
  labs(title = "Co-occurrence Network of Key Themes")
```

>>>>

```{r R Load Libraries, Directories, and Datasets}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(igraph)
library(ggraph)
library(tidytext)
library(topicmodels)
library(visNetwork)
library(RColorBrewer) 
library(sjPlot)
library(ldatuning)
library(tm)
library(SnowballC)

@@

```{r Filtering For Relevancy}
# Calculate the minimum and maximum of the 'Thread_Relevancy' column
min_value <- min(all_threads$Thread_Relevancy, na.rm = TRUE)
max_value <- max(all_threads$Thread_Relevancy, na.rm = TRUE)

@@

```{r Filtering Out Quartile 1}
filtered_threads <- all_threads %>%
  filter(Quartile != "Q1")

@@

```{r Relevancy Filtered Descriptive Statistics}
# Step 1: Group by newsgroup and calculate required statistics, including comment relevancy
keywords_summary_df <- filtered_comments %>%
  group_by(newsgroup) %>%
  summarize(
    Unique_Authors = n_distinct(Author),
    Comments_with_Keywords = sum(Relevancy > 0),
    Conversations_Mentioned_In = n_distinct(Thread.ID),
    Total_Comments_In_Threads = n(),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Relevancy, na.rm = TRUE)
  )

@@

# Theme Prevelance Hypothesis
```{r Data Preparation}
# Data preparation: Select relevant text data
comments_corpus <- Corpus(VectorSource(filtered_comments$Full.Text)) # Replace 'Content' with the actual column name containing text data

@@

```{r How Many Topics, eval=FALSE, include=FALSE}
# Optimize LDA to find the best number of topics
set.seed(123)
result <- FindTopicsNumber(
  dtm,
  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
  metrics = c("Griffiths2004", "Deveaud2014"),  # Use fewer metrics
  method = "Gibbs",
  control = list(seed = 123, iter = 500),  # Fewer iterations for quicker results
  mc.cores = 6L,
  verbose = TRUE
)

@@

```{r LDA Model}
set.seed(123) # Set seed for reproducibility
lda_model <- LDA(dtm, k = 5, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
```

@@

```{r Improved Co-occurrence Network Analysis}
library(ggforce)
library(ggrepel)
library(ggplot2)
library(igraph)

# Step 1: Calculate Term Frequencies and Filter for Top Terms
co_occurrence <- crossprod(as.matrix(dtm)) # Create co-occurrence matrix
# Set a threshold to filter less relevant terms based on frequency
term_frequency <- rowSums(co_occurrence) # Calculate term frequency
threshold <- quantile(term_frequency, 0.75) # Set threshold for top 25% most frequent terms
filtered_terms <- which(term_frequency > threshold)
filtered_co_occurrence <- co_occurrence[filtered_terms, filtered_terms]

# Step 2: Create a Graph Object with Filtered Terms
graph <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)

# Step 3: Simplify the Graph to Avoid Self-Loops and Redundant Edges
graph <- simplify(graph)

# Step 4: Assign Topics to Terms Based on the LDA Model
terms <- rownames(filtered_co_occurrence) # Extract terms from the filtered co-occurrence matrix
term_topic_probs <- posterior(lda_model)$terms[, terms] # Extract term-topic probabilities for the filtered terms
term_topic_assignment <- apply(term_topic_probs, 2, which.max) # Assign each term to the topic with the highest probability

# Create a data frame mapping terms to topics
term_topic_df <- data.frame(term = terms, topic = factor(term_topic_assignment))

# Increase the repulsion and area in the layout algorithm
set.seed(123)  # For reproducibility
graph_layout <- create_layout(graph, layout = layout_with_fr(graph, niter = 5000, area = vcount(graph)^3.5, repulserad = vcount(graph)^3.5))

# Normalize the layout to ensure it fits within the plot
graph_layout$x <- scale(graph_layout$x, center = TRUE, scale = TRUE) * 4  # Increase spread
graph_layout$y <- scale(graph_layout$y, center = TRUE, scale = TRUE) * 4  # Increase spread

# Create intuitive topic names based on LDA results
topic_names <- c(
  "Medical Testing & Treatment",
  "Personal Experiences & Opinions",
  "Disease Research & Transmission",
  "Sexual Orientation & Behavior",
  "Social Discussion & Impact"
)
term_topic_df$topic_name <- topic_names[term_topic_df$topic]

# Create the improved plot with simplified legend
co_occurrence_plot <- ggplot(graph_layout, aes(x = x, y = y)) +
  geom_edge_link(aes(edge_alpha = weight), edge_width = 0.3, color = "gray70", alpha = 0.3) +
  geom_node_point(aes(size = log1p(term_frequency[filtered_terms]), color = term_topic_df$topic_name), show.legend = TRUE, alpha = 0.8) +
  geom_text_repel(aes(label = name), 
                  max.overlaps = 20,
                  force = 10,
                  point.padding = 0.5,
                  segment.color = "gray50",
                  min.segment.length = 0,
                  box.padding = 0.7,
                  segment.size = 0.2,
                  size = 8) +
  geom_mark_hull(aes(group = term_topic_df$topic_name, fill = term_topic_df$topic_name), 
                 alpha = 0.1, show.legend = FALSE) +
  scale_size(range = c(2, 12), name = "Term Frequency") +
  scale_color_brewer(palette = "Set1", name = "Topic") +
  scale_fill_brewer(palette = "Set1", guide = "none") +  # Remove fill from legend
  coord_cartesian(xlim = c(-7.5, 7.5), ylim = c(-7.5, 7.5)) +
  theme_void(base_size = 16) +
  theme(
    aspect.ratio = 1,
    legend.position = "right",
    legend.box = "vertical",
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    plot.margin = margin(40, 40, 40, 40),
    plot.background = element_rect(fill = "white", color = NA),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12)
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  labs(title = "Co-occurrence Network of Key Themes in AIDS Discussion",
       caption = "Node size represents term frequency. Colors indicate topics identified by LDA.")

# Display the plot
print(co_occurrence_plot)

# Save the plot to a PNG file with increased size
ggsave(file.path(output_directory, "images and tables", "co-occurrence_network.png"), 
       plot = co_occurrence_plot, width = 20, height = 16, dpi = 300)  # Increased dimensions
```

### 2024-09-01 Scripts - Data Cleaning and Visuals/Webpage Visualizations.Rmd
finished the first hyp code

---
title: "Web Page Visualization Code"
author: "Emerson Johnston"
lastmodifeddate: "2024-08-24"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

# Load the datasets with the correct file paths
all_threads = pd.read_csv(os.path.join(threads_directory, "threads_cleaned_82TO89.csv"))
all_comments = pd.read_csv(os.path.join(comments_directory, "comments_cleaned_82TO89.csv"))
```

>>>>

---
title: "Web Page Visualization Code"
author: "Emerson Johnston"
lastmodifeddate: "2024-09-01"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

# Load the datasets with the correct file paths
all_threads = pd.read_csv(os.path.join(threads_directory, "aids_related_threads_82TO86.csv"))
all_comments = pd.read_csv(os.path.join(comments_directory, "aids_related_comments_82TO86.csv"))
```
